Simplifying Parallel Graph Processing

### 2016-12-09 report/survey.tex
Got survey into ACM sig proceedings format.
Tweaked get-hwinfo and the specs to be easier to fit in 2-column
mode. Got tools table to be two columns wide.

Added sty and cls files necessary for ACM format.

\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in, headheight=15pt]{geometry}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

\usepackage{fancyhdr, setspace}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\setlength{\headheight}{15pt} % Removes warnings. Set to 30pt if 2 lines on the header.
\lhead{}
\rhead{}
\usepackage{totcount}
\regtotcounter{page}
\cfoot{\ifnum\totvalue{page} > 1 \thepage \else\fi}

@@

\begin{document}
\title{Simplifying Parallel Graph Processing: \\
	\large Survey of Existing Platforms
}
\author{Samuel Pollard (\href{mailto:spollard@cs.uoregon.edu}{spollard@cs.uoregon.edu})}
\date{\today}
\maketitle

This is a survey of existing graph analytics frameworks.

@@

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table}[!htb]
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		% \small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table}

@@

\bibliographystyle{acm}
\bibliography{drp}

\end{document}

>>>>

\documentclass{sig-alternate}
%\documentclass[11pt]{article}
%\usepackage[margin=1in, headheight=15pt]{geometry} % No geometry with sig-alternate
%\usepackage{fancyhdr, setspace}
%\renewcommand{\headrulewidth}{0pt}
%\pagestyle{fancy}
%\setlength{\headheight}{15pt} % Removes warnings. Set to 30pt if 2 lines on the header.
%\lhead{}
%\rhead{}
%\usepackage{totcount}
%\regtotcounter{page}
%\cfoot{\ifnum\totvalue{page} > 1 \thepage \else\fi}
%\usepackage{amsmath, amsthm, amsfonts}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

@@

\begin{document}
%%% ACM title stuff %%%
\setcopyright{acmcopyright}
\doi{?}
\isbn{?}
%\acmPrice{}
\conferenceinfo{Load Testing and Benchmarking of Software Systems (LTB)}{2017, L'Aquila, Italy}
\title{Simplifying Parallel Graph Processing}
\subtitle{A Survey of Existing Platforms}
\numberofauthors{2}
\author{
\alignauthor
	Samuel Pollard\\
	\affaddr{University of Oregon}\\
	\affaddr{Eugene, OR, USA}\\
	\email{spollard@cs.uoregon.edu}
\alignauthor
	Boyana Norris\\
	\affaddr{University of Oregon}\\
	\affaddr{Eugene, OR, USA}\\
	\email{norris@cs.uoregon.edu}
}
% Generated from http://dl.acm.org/ccs/ccs.cfm
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10011007.10010940.10011003.10011002</concept_id>
	<concept_desc>Software and its engineering~Software performance</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Software performance}

%%% Normal title stuff %%%
%\title{Simplifying Parallel Graph Processing: \\
%	\large Survey of Existing Platforms
%}
%\author{Samuel Pollard (\href{mailto:spollard@cs.uoregon.edu}{spollard@cs.uoregon.edu})}
%\date{\today}
\maketitle

\begin{abstract}
This is a survey of existing graph analytics frameworks.
\end{abstract}

@@

\section{Graph Processing Taxonomy}
This is in the spirit of \cite{Doekemeijer:2015:GPFSurvey}. Here, ``|'' means ``or'' and ``+'' means ``and.'' FOSS means Free and Open Source Software. The quotes around ``yes'' for HPC mean that the product claims to be amenable to high performance computing. Whether these actually achieve their goal is one of the purposes of this project.
\begin{table*}[t]
	\begin{minipage}{\linewidth} % So the footnotes all get printed on the same page
		\centering
		%\small
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={Name,Type,HPC,Parallelism,Target,FOSS,Source,Notes},
			every head row/.style={after row=\midrule},
			columns/Name/.style={string type, column type={l|}},
			columns/Type/.style={string type},
			columns/HPC/.style={string type},
			columns/Parallelism/.style={string type},
%			columns/Comm./.style={%
%				string type,
%				postproc cell content/.style={%
%					@cell content/.add={\footnotesize}
%				}
%			},
			columns/Target/.style={string type},
			columns/FOSS/.style={string type},
			columns/Source/.style={string type},
			columns/Notes/.style={
				preproc cell content/.style={@cell content=
					\ifx&##1&% Only make a footnote if the cell is nonempty
						##1
					\else
						\footnote{##1}
					\fi}
			},
		]{platforms.csv}
		\caption{Tools used for graph processing}
		\label{tab:frameworks}
	\end{minipage}
\end{table*}

@@

%\bibliographystyle{acm}
\bibliographystyle{abbrv}
\bibliography{drp}
\end{document}
